---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# croquet

<!-- badges: start -->
[![Lifecycle:
experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN
status](https://www.r-pkg.org/badges/version/gtreg)](https://CRAN.R-project.org/package=gtreg)
<!-- badges: end -->

A collection of clinical research organization (CRO) miscellaneous functions 
developed for [The Prostate Cancer Clinical Trials Consortium (PCCTC)](http://pcctc.org/).

## Installation

⚠️ This package is under active development! Feedback is welcome, consistency is not yet promised.

You can install the development version of croquet from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("pcctc/croquet")
```

## Exporting labelled data

This is a basic example which shows you how to solve a common problem:

```{r example}
library(croquet)
## basic example code
```

## Code of Conduct

Please note that the gtreg project is released with a [Contributor Code
of
Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.

```{r, echo = FALSE}
knitr::knit_exit()
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
