---
title: "{{folder_name}}"
subtitle: "Medidata Setup"
date: "`r Sys.Date()`"
format:
  html:
    page-layout: full
    theme: united
    toc: true
    toc-float: true
    toc-depth: 2
    toc-location: left
embed-resources: true
execute: 
  echo: true
---

```{r setup}
#| include: false
set.seed({{format(Sys.Date(), format = "%Y%m%d")}})
options(subdir_name = "{{folder_name}}", openxlsx.dateFormat = "yyyy-mm-dd")
```

1. Import all raw Medidata data sets into a list

1. Clean each of the Medidata data sets individually as needed. There are no changes to the structure of these data sets in this step, meaning that if a raw data set is one line per person per AE, the cleaned data set will have the same structure.

1. The RAW Medidata is imported as a named list. After an individual data set is cleaned/checked, it is added to a named list.

# Raw Data Import

```{r import}
library(dsverse); library(tidyverse)

# setting MSK ggplot theme, gtsummary theme, and color palette
theme_set(mskRvis::theme_biostat()); theme_gtsummary_pcctc(); mskRvis::set_msk_palette()

# import sas files
lst_medidata_raw_data <-
  read_sas_batch(here_data("medidata")) %>%
  prepare_raw_medidata()

names(lst_medidata_raw_data)

# save cleaned medidata files into this named list.
lst_medidata_data <- list()

```

# Clean each Medidata Data Set

```{r cleaning}

```

# Save Analytic Data

```{r save}
#saving cleaned Medidata files
saveRDS(lst_medidata_data, file = here_data("derived-data", "medidata-cleaned.RDS"))
```
